\documentclass[11pt]{exam}
\printanswers
\usepackage{amsmath,amssymb,complexity}
\usepackage{datetime,enumerate,palatino}
\usepackage{setspace}

\newcommand{\N}{{\mathbb{N}}}
\newcommand{\bool}{\{0,1\}}
\newcommand{\owf}{\mathsf{OWF}}
\newcommand\myeq{\mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\tiny\sffamily def}}}{=}}}
\begin{document}
\setstretch{1.1}

\hrule
\vspace{3mm}
\noindent
{\sf IITM-CS6111 : Foundations of Cryptography  \hfill Assignment \#2 }
\vspace{3mm} \\
\noindent
{\sf Topic: One-way functions \hfill Due on : $14^{th}$ Dec, 2020}
\vspace{3mm}
\hrule

{\small 
\begin{itemize}
\itemsep 0pt
\item All answers must be written in mathematically rigorous form.
\item Use LaTeX to generate the pdf file of your solution. \textbf{NO} photographs/scanned copies of hand written solutions are accepted. 
\item Students are allowed to form groups (maximum of $3$ members) for this assignment. However, referring to internet etc is strictly disallowed.
\item Submit solutions at moodle link before the deadline one per team. Clearly mention the names and roll numbers of all the teammates involved.
\end{itemize}
}
% uncomment the lines below and fill name and roll number of teammates here

%\hrule
%\vspace{3mm}
%\noindent
%{\sf Roll No: \hfill Full Name: } 
%\vspace{3mm}\\
%\noindent
%{\sf Roll No: \hfill Full Name: } 
%\vspace{3mm}\\
%\noindent
%{\sf Roll No: \hfill Full Name: } 
%\vspace{3mm}

\hrule

\begin{questions}

\question[10] 
Prove that there is no one-way function $f\colon\bool^n\to \bool^{\lfloor \log n \rfloor}$.
%\begin{solution}
%    Uncomment the lines above and below and write your solution here
%\end{solution}
\question[10]

Prove or disprove: If $f:\bool^n\to\bool^n$ is a one-way function, then the function $g:\bool^n\to\bool^{n-\lfloor \log n \rfloor}$ which outputs the $n-\lfloor \log n \rfloor$ higher order bits of $f$ is also a one-way function. (i.e $\forall x \in \bool^n$, if $f(x)=b_1b_2\cdots b_n$ then $g(x)=b_1b_2\cdots b_{n-\lfloor \log n \rfloor}$)
%\begin{solution}
%    Uncomment the lines above and below and write your solution here
%\end{solution}

\question[10]({\bf Expanding $\owf$s}) Prove that if $f$ is a one-way function, then the function $g$ defined by $g(x_1,x_2)\myeq\left(f(x_1),x_2\right)$ where $|x_1|=|x_2|$, is also a one-way function. Observe that $g$ reveals half of its input, but is nevertheless one-way.
%\begin{solution}
%    Uncomment the lines above and below and write your solution here
%\end{solution}

\question[10]({\bf Composition of $\owf$s}) Let $f$ be a one-way function. Is $g(x)\myeq f(f(x))$ necessarily a one-way function? What about $g'(x)\myeq f(x)||f(f(x))$? Prove your answers.
%\begin{solution}
%    Uncomment the lines above and below and write your solution here
%\end{solution}

\question[10]({\bf Length preserving $\owf$}) Prove that if there exists a one way function, then there exists a length preserving one-way function.

\emph{Hint: Let $f$ be a one-way function and and let $p(.)$ be a polynomial such that $|f(x)|\leq p(|x|)$. (Justify the existence of $p$.) Define $f'(x)\myeq f(x)||10^{p(|x|)-|f(x)|}$. Further modify $f'$ to get a length-preserving function that remains one-way.}
%\begin{solution}
%    Uncomment the lines above and below and write your solution here
%\end{solution}

\end{questions}
\end{document}


